\begin{biblio}

\bibitem{Dmitruk2004}
Габасов Р., Н.М. Дмитрук, Ф.М. Кириллова. Оптимальное управление многомерными системами по неточным измерениям их выходных сигналов // Труды Института математики и механики УрО РАН, Т.10, №2, 2004. С. 33-57.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%liza's

\bibitem{Berberich}
Berberich, J. A trajectory-based framework for data-driven system analysis and control /
J. Berberich, F. Allg{\"o}wer //
arXiv: 1903.10723. -- 2019.

\bibitem{BerberichRobust} 
Berberich, J. Robust data-driven state-feedback design /
J. Berberich, A. Romer, C. W. Scherer, F. Allg{\"o}wer //
arXiv: 1909.04314. -- 2019.

\bibitem{BerberichMPC}
Berberich, J. Data-Driven Model Predictive Control with Stability and Robustness Guarantees /
J. Berberich, J. K{\"o}hler, M. A. M{\"u}ller, F. Allg{\"o}wer //
arXiv: 1906.04679. -- 2019.

\bibitem{Copp}
Copp, D. Simultaneous nonlinear model predictive control and state estimation /
D. Copp, J. Hespanha //
Automatica. -- 2016. -- Vol.~77. -- P.~{143-154}.

\bibitem{Coulson}
Coulson, J. Data-Enabled Predictive Control: In the Shallows of the DeePC / 
J. Coulson, J. Lygeros, F. D{\"o}rfler // 18th European Control Conference (ECC), Naples, Italy. --  2019. -- P.~307-312.

\bibitem{Review}
Hou, Z.-S. From model-based control to data-driven control: Survey, classification and perspective / Z.-S Hou, Z. Wang // Information Sciences. -- 2013. -- Vol.235. -- P.3-35.

\bibitem{Persis}
De Persis, C. Formulas for data--driven control: Stabilization, optimality and robustness /
C. De Persis, P. Tesi //
arXiv: 1903.06842. -- 2019.

\bibitem{Romer}
Romer, A. One--shot verification of dissipativity properties from input--output data /
A. Romer, J. Berberich, J. K{\"o}hler, F. Allg{\"o}wer //
IEEE Control Systems Letters. -- 2019. -- Vol.~3, no.3. -- P.~709-714.

\bibitem{Waarde}
Waarde, H.J. Data informativity: a new perspective on data-driven analysis and control /
H. J. van Waarde, J. Eising, H. L. Trentelman, M. K. Camlibel //
arXiv: 1908.00468. -- 2019.

\bibitem{Willems}
Willems, J. C. A note on persistency of excitation /
J. C. Willems, I. Markovsky, P. Rapisarda, B. L. M. De Moor // 
Systems \& Control Letters. -- 2005. -- Vol.~54. -- P.~325-329.

%\bibitem{WillemsPuzzles}
%Willems, J. C. Paradigms and puzzles in the theory of dynamical systems / IEEE Transactions on Automatic Control. -- 1991. -- Vol.~36, no~3. -- P.259-294.
\end{biblio} 